\textbf{Optimization of Porous Silicon Gradient Refractive Index Structures.}

### 2020-09-18 paper.tex
Small corrections and changes

  \nabla^2\phi=-4\pi q_0\delta(\bm r-\bm r_0),

@@

@@

We consider first a system made of identical {\em unit} charges
ocuppying the positions $\bm R$ of a 2D Bravais lattice $\{\bm R\}$,
which we will take as a rectangular lattice with lattice parameters
$2a$ and $2b$, and lying, for the time being, at the $z=0$ plane.
The potential it produces obeys
\begin{equation}
  \label{eq:poissonRed}
  \nabla^2\phi(\bm r)=-4\pi\sum_{\bm R}\delta(\bm r_\|-\bm
  R)\delta(z)=-\frac{4\pi}{A}\sum_{\bm G}e^{i\bm G\cdot\bm r_\|}\delta(z),
\end{equation}
where $\bm r_\|$ is the projection of the observation position $\bm
r=(x,y,z)$ onto the $xy$ plane,
$\delta(\ldots)$ is Dirac's delta function, $\{\bm G\}$ is the
reciprocal lattice defined through $e^{i\bm G\cdot\bm R}=1$ for all
$\bm R$ and $\bm G$, $A=4ab$ is the area of the unit cell
and we used the Fourier representation of the 2D
periodically repeated delta function. We introduce a 2D Fourier representation for
the potential
\begin{equation}
  \label{eq:phifourier}
  \phi(\bm r)=\sum_{\bm G}\phi_{\bm G}(z)e^{i\bm G\cdot\bm r_\|}
\end{equation}
where $\phi_{\bm G}(z)$ is the Fourier coefficient of the potential at
the height $z$. Substitution in Eq. \eqref{eq:poissonRed} yields the
ordinary differential equation
 \begin{eqnarray}
 \frac{d^2}{dz^2}\phi_{\bm G}(z)-G^2\phi_G(z)=
   -\frac{4 \pi}{A} \delta(z),
 \end{eqnarray}
for each coefficient, an homogeneous equation for $z\ne0$ which may be trivially
solved. After applying boundary conditions at $z=0$ and regularity
conditions at infinity, we obtain
\begin{equation}
  \label{eq:phiG}
  \phi_{\bm G}(z)=
  \begin{cases}
    -\dfrac{2\pi}{A}\abs{z}&\text{if }G=0,\\
    \dfrac{2 \pi}{AG}  e^{- G \abs{z}}&\text{if }G\neq 0.
  \end{cases}
\end{equation}
The case $G=0$ corresponds to the potential produced by a uniformly charged plane,
while the case $G\ne 0$ is the potential produced by a sinusoidal
charge density on a plane, given by the
symmetric solution that decays exponentially as we get away, upwards
or downwards, from
the source plane. Substituting into Eq. \eqref{eq:phifourier} yields
\begin{eqnarray}
  \label{eq:phiG1}
 \phi(\bm r) = -\frac{2 \pi}{A}  \abs{z} +{\sum_{\bm G}}' \frac{2 \pi
   }{AG} e^{- G \abs{z}} e^{i \bm G\cdot\bm r_\|},
 \end{eqnarray}
where the prime indicates that the term $G=0$ should be ommited from
the sum.

@@

\subsection{Reflectance Measurement}
\label{sec:refl-meas}
We measured the reflectivity spectra at different positions over our
samples using a {\em Perkin Elmer Lambda 950}
UV-Vis-NIR spectrophotometer.\notaL{Finalmente, ¿fue éste el que se
  usó? Si sí, ¿hay algo internesante que decir sobre el? Cosas como el
tamaño de mancha, resolución espectral, etc.} For interpretation of the
data layer we used
the standard formula \cite{T8,T9} for the reflectance of three media:
air (0) environment, the PS film (1) and the c-Si substrate (2),
 \begin{equation}\label{Eq:ECMR}
   R=\left |\frac{r _ {_ {01}}r _ {_ {12}} e^{2i\delta}}{1+r _ {_
   {01}}r _ {_ {12}} e^{2i\delta}}\right |^2
\end{equation}
where $r_{01}$ and $r_{12}$ are the Fresnel reflectance
coefficients of the air/PS and PS/c-Si interfaces \cite{T10,T11}
and $\delta=k_1^\perp d$, where $k_1^\perp$ is
the component of the wavevector perpendicular to the surface within
the porous layer of thickness $d$. The reflectance depends on the
thickness of the film and on the index of refraction $n_1=n_{\text{PS}}$ of the porous
layer, which we relate to the porosity through Bruggeman's
effective medium theory \cite{I20},
\begin{equation}\label{Eq:Brugg}
 p\frac{1-\epsilon_1} {1+\epsilon_1} + (1-p)
  \frac{\epsilon_2 - \epsilon_1}
  {\epsilon_2+\epsilon_1}=0,
\end{equation}
where $\epsilon_2=\epsilon_{\text{Si}}$ is the dielectric function of
the c-Si substrate, and
$\epsilon_1=n_{\text{PS}}^2$ is the dielectric function of the PS layer.
We fitted the reflectance spectra using the porosity $p$ and the
thickness $d$ and a scale calibration factor $s$ as fitting
parameters, and thus, we obtained the porosity
$p$ and the etching rate $v=d/t$ for different values of the local
current density $j_\perp$ expected at several positions on different
samples.

@@

From Eq. \eqref{Eq:J} we evaluate the
normalized current density $j_\perp/I$ expected at the positions $n$ indicated in
Fig. \ref{fig:SI3}.
(Table \ref{t:xj}).
\begin{table}
  \centering
  \begin{tabular}{rrr}
    \(x'_n\)(cm) & \(x\)(cm)& \(j_\perp/I\) (\(\text{cm}^{-2})\)\\
    from edge& from wall&\\
    \hline
    0.2 & 0.06 & 0.7219\\
    0.4 & 0.26 & 0.6723\\
    0.6 & 0.46 & 0.5769\\
    0.8 & 0.66 & 0.4645\\
    1.0 & 0.86 & 0.3599\\
    1.2 & 1.06 & 0.2749\\
    1.4 & 1.26 & 0.2112\\
    1.6 & 1.46 & 0.1666\\
  \end{tabular}
  \caption{Normalized current density $j_\perp/I$ expected at different positions $x'_n$.}
  \label{t:xj}
\end{table}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{R5vslambda}
  \caption{Reflectance spectra at different positions
    on sample $G_1$ ($I_1=5\,\text{mA}$), where
    $x'_n=0.2-1.6\,\text{cm}$ and $y=0.74\,\text{cm}$. We show
  experimental results and results fitted through
  equations~\eqref{Eq:ECMR} and \eqref{Eq:Brugg}}.
  \label{fig:R5}
\end{figure}
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{R10vslambda}
  \caption{Reflectance spectra at different positions
    on sample $G_2$ (shown in Fig. \ref{fig:SI3}), where
    $x'_n=0.2-1.6\,\text{cm}$ and $y=0.74\,\text{cm}$. We show
  experimental results and results fitted through
  equations~\eqref{Eq:ECMR} and \eqref{Eq:Brugg}}.
  \label{fig:R10}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{R20vslambda}
  \caption{Reflectance spectra at different positions
    on sample $G_3$ (shown in Fig. \ref{fig:SI3}), where
    $x'_n=0.2-1.6\,\text{cm}$ and $y=0.74\,\text{cm}$. We show
  experimental results and results fitted through
  equations~\eqref{Eq:ECMR} and \eqref{Eq:Brugg}}.
  \label{fig:R20}
\end{figure}

We measured the reflectance spectra  at the positions indicated in
Fig. \ref{fig:SI3} on our three samples $G_1$, $G_2$,
and$G_3$, prepared using the same procedure
(Sec. \ref{sec:fabrication-ps-grin}) but applying different currents
$I_1=5\,\text{mA}$, $I_2=10\,\text{mA}$, and $I_3=20\,\text{mA}$, . The results are shown in
Figs. \ref{fig:R5}, \ref{fig:R10}, and \ref{fig:R20}.
We fitted the reflectance measurements using Eqs. \eqref{Eq:ECMR} and
\eqref{Eq:Brugg} using the local porosity $p$, and the thickness of the
film  $d$ as
adjustable parameters. We also fitted a scaling parameter $s$ to allow
for calibration variations among spectra. From the thickness we
obtained the etching rate $v=d/t$ at each position. Notice that the fit is reasonably
good. The contrast of the reflectance in the experiment is somewhat smaller
than in our fitted curves. We believe this is due to the finite width
\notaL{beams width=?} of the illuminating beam of our
spectrometer. Thus, as our GRIN sample is not macroscopically homogeneous and its
properties have a gradient, the
experimental results have contributions from regions with slightly
different porosities and thicknesses, averaging out the interference
maxima and minima. We also expect microscopic inhomogeneities such as
interface roughness that might also reduce the contrast.
This is most notable for the thicker regions
towards the left side of Fig. \ref{fig:SI3} and for smaller
wavelengths.

@@

\begin{table}
\centering
\begin{tabular}{lrrrrrr}
  Sample/ & position & density & porosity &
  thickness & scale & etching rate\\
  $I$ (mA) &$x'_n$ (cm)&  $j$ ($\text{mA}/\text{cm}^2$) & $p$
       & $d$ ($\mu\text{m}$) & $s$ & $v$ (nm/s)\\
\hline
$G_1$/ 5 &0.2 & 3.609 & 0.4943 & 0.3402 & 0.8493&  1.3608 \\
         &0.4 & 3.361 & 0.5713 & 0.3895 & 0.9789&  1.558  \\
         &0.6  & 2.884 & 0.5657 & 0.3312 & 0.9569&  1.3248 \\
         &0.8 & 2.322 & 0.5555 & 0.2732 & 0.9536&  1.0928 \\
         &1.0 & 1.799 & 0.5592 & 0.2236 & 0.9951&  0.8944 \\
         &1.2 & 1.374 & 0.5557 & 0.1886 & 0.9729&  0.7544 \\
         &1.4 & 1.056 & 0.5491 & 0.1512 & 0.9606&  0.6048 \\
         &1.6 & 0.833 & 0.5519 & 0.1238 & 0.9897&  0.4952 \\
$G_2$/10&0.2 & 7.219 & 0.5910 & 0.6347 & 0.8559&  2.5388 \\
         &0.4 & 6.723 & 0.6437 & 0.6934 & 0.9914&  2.7736 \\
         &0.6 & 5.769 & 0.6383 & 0.5907 & 0.9523&  2.3628 \\
         &0.8 & 4.645 & 0.6265 & 0.5327 & 0.9798&  2.1308 \\
         &1.0 & 3.599 & 0.5991 & 0.4587 & 0.9389&  1.8348 \\
         &1.2 & 2.749 & 0.5902 & 0.4044 & 0.9449&  1.6176 \\
         &1.4 & 2.112 & 0.5753 & 0.3378 & 0.9361&  1.3512 \\
         &1.6 & 1.666 & 0.5711 & 0.2958 & 0.9481&  1.1832 \\
$G_3$/20 &0.2 & 14.438& 0.6860 & 1.2044 & 1.1491&  4.8176 \\
          &0.4 & 13.44 & 0.7129 & 1.1931 & 1.0767&  4.7724 \\
          &0.6 &11.538 & 0.7031 & 1.0443 & 1.0588&  4.1772 \\
          &0.8 & 9.29  & 0.6258 & 0.7516 & 1.0063&  3.0064 \\
          &1.0 & 7.198 & 0.6247 & 0.5380 & 1.0104&  2.152  \\
          &1.2 & 5.498 & 0.5927 & 0.4387 & 0.9625&  1.7548 \\
          &1.4 & 4.224 & 0.5844 & 0.3633 & 0.9625&  1.4532 \\
          &1.6 & 3.332 & 0.5909 & 0.3392 & 1.0112&  1.3568 \\
\end{tabular}
\caption{\label{t:jpdv}
  Current density and fitted parameters for saveral positions on
  three samples:  porosity, thickness, scale factor and etching rate.}
\end{table}

From the data in Table \ref{t:jpdv} we can plot the fitted porosity as
a function of the calculated density current, as shown for our three
samples in Fig. \ref{fig:p}.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{pvsj}
  \caption{Porosity as a function of current density for three samples
    $G_1$, $G_2$, $G_3$. The data points for each sample are joined by
    thick lines. The arrows point to data that correspond to
    position $x'_1=0.2\,\text{cm}$, joined to the other data by a thin
    line (see text). We include linear fits to the data from
    sample $G_3$ (thick straight line) and to that from all the
    samples (thin straight line). }
  \label{fig:p}
\end{figure}
Notice that for each sample the data points lie around straight lines,
except for one outlier point in each corresponding to position
$x'_1$. As discussed in Sec. \ref{sec:ps-grin-single}, those points
were very close to a wall of the electrolytic cell, so they were
affected by leakage currents towards the underside of the wall.
For this reason, we exclude those points from the following
analysis. We made a linear fit to the data from sample $G_3$ and to
the data from the three samples. A comparison shows that a fit to the
data of just one sample, $G_3$, turns out to be a reasonable predictor for the
porosity of all the samples.  From that fit we obtain that for our
preparation conditions
\begin{equation}\label{eq:p}
  p\approx 0.013\frac{\text{cm}^2}{\text{mA}} j_\perp+0.53.
\end{equation}

Similarly, we can plot the fitted etching rate as
a function of the calculated density current, as shown for our three
samples in Fig. \ref{fig:v}.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{vvsj}
  \caption{Etching rate as a function of current density for three samples
    $G_1$, $G_2$, $G_3$. The data points for each sample are joined by
    thick lines. The arrows point to data that correspond to
    position $x'_1=0.2\,\text{cm}$, joined to the other data by a thin
    line (see text). We include linear fits to the data from
    sample $G_3$ (thick straight line) and to that from all the
    samples (thin straight line). }
  \label{fig:v}
\end{figure}
As for the porosity, there are outlier points corresponding to the
immediate proximity of the wall of the cell, but the remaining points
lie on straight lines for each sample, and they
may all be approximated by a linear fit to the data of just one
sample, $G_3$, from which we get
\begin{equation}\label{eq:v}
  v\approx 0.35\frac{\text{cm}^2}{\text{mA}}
  \frac{\text{nm}}{\text{s}}j_\perp + 0.092\frac{\text{nm}}{{s}}.
\end{equation}

Using Eqs. \eqref{eq:p}, \eqref{eq:v}, \eqref{Eq:ECMR}, and
\eqref{Eq:Brugg}, we can calculate the reflectance spectra for any
desired current density $j_\perp$ and etching time. This is
illustrated in Fig. \ref{fig:Rvsjl} for the parameters that correspond
to our samples.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{jlr}
  \caption{Reflection $R$ of a PS film as a function of the current density
    current $j_\perp$ and wavelength $\lambda$ for an etching time
    $t=250\,\text{s}$. Theory (left panel) and experiment (right
    panel, see text). We indicate with the numbers 1, 2, 3 the
    data corresponding to the corresponding samples $G_1$, $G_2$ and
    $G_3$.}
  \label{fig:Rvsjl}
\end{figure}
On the right hand side of the figure we display a quilt made by
patching together the experimental reflectance data corresponding to
Figs. \ref{fig:R5}- \ref{fig:R20}, ordered according to the
corresponding current density as presented in Table
\ref{t:jpdv}. Nevertheless, for the reasons mentioned above, we
eliminated the data corresponding to position $x'_1$ on all
samples. Furthermore, as the results corresponding to sample $G_2$ in
Figs. \ref{fig:p} and  \ref{fig:v} seem shifted with respect to those
of the other samples, in order to facilitate the visualization of the
results, we artificially shifted horizontally towards the
right their contributions to Fig. \ref{fig:Rvsjl} by
$1\,\text{mA}/\text{cm}^2$. Notice that the experimental results may
be grouped along bright and dark bands and that they correspond closely to
those expected theoretically, though the experimental bands are somewhat shifted,
especially for low current densities, and the minima are not as low.

The theoretical reflectance coudl as well be calculated using
Eqs. \eqref{eq:p}, \eqref{eq:v}, \eqref{Eq:ECMR}, and
\eqref{Eq:Brugg}, for more complicated structures, in which the
current $I$ is modulated in time, allowing the design and analysis of
non-trivial multilayered GRIN PS structures.

>>>>

  \nabla^2\phi=-4\pi q_0\delta^{(3)}(\bm r-\bm r_0),

@@

Here, $\delta^{(D)}$ is Dirac's delta function in $D$ dimensions.

@@

We consider first a system made of identical {\em unit} charges
ocuppying the positions $\bm R$ of a 2D Bravais lattice $\{\bm R\}$,
which we will take as a rectangular lattice with lattice parameters
$2a$ and $2b$, and lying, for the time being, at the $z=0$ plane.
The potential it produces obeys
\begin{equation}
  \label{eq:poissonRed}
  \nabla^2\phi(\bm r)=-4\pi\sum_{\bm R}\delta^{(2)}(\bm r_\|-\bm
  R)\delta^{(1)}(z)=-\frac{4\pi}{A}\sum_{\bm G}e^{i\bm G\cdot\bm r_\|}\delta^{(1)}(z),
\end{equation}
where $\bm r_\|$ is the projection of the observation position $\bm
r=(x,y,z)$ onto the $xy$ plane, $\{\bm G\}$ is the
reciprocal lattice defined through $e^{i\bm G\cdot\bm R}=1$ for all
$\bm R$ and $\bm G$, $A=4ab$ is the area of the unit cell
and we used the Fourier representation of the 2D
periodically repeated delta function. We introduce a 2D Fourier representation for
the potential
\begin{equation}
  \label{eq:phifourier}
  \phi(\bm r)=\sum_{\bm G}\phi_{\bm G}(z)e^{i\bm G\cdot\bm r_\|}
\end{equation}
where $\phi_{\bm G}(z)$ is the Fourier coefficient of the potential at
the height $z$. Substitution in Eq. \eqref{eq:poissonRed} yields the
ordinary differential equation
 \begin{eqnarray}
 \frac{d^2}{dz^2}\phi_{\bm G}(z)-G^2\phi_G(z)=
   -\frac{4 \pi}{A} \delta^{(1)}(z),
 \end{eqnarray}
for each coefficient, an homogeneous equation for $z\ne0$ which may be trivially
solved. After applying boundary conditions at $z=0$ and regularity
conditions at infinity, we obtain
\begin{equation}
  \label{eq:phiG}
  \phi_{\bm G}(z)=
  \begin{cases}
    -\dfrac{2\pi}{A}\abs{z}&\text{if }G=0,\\
    \dfrac{2 \pi}{AG}  e^{- G \abs{z}}&\text{if }G\neq 0.
  \end{cases}
\end{equation}
The case $G=0$ corresponds to the potential produced by a uniformly charged plane,
while the case $G\ne 0$ is the potential produced by a sinusoidal
charge density on a plane, given by the
symmetric solution that decays exponentially as we get away, upwards
or downwards, from
the source plane. Substituting into Eq. \eqref{eq:phifourier} yields
\begin{eqnarray}
  \label{eq:phiG1}
 \phi(\bm r) = -\frac{2 \pi}{A}  \abs{z} +{\sum_{\bm G}}' \frac{2 \pi
   }{AG} e^{- G \abs{z}} e^{i \bm G\cdot\bm r_\|},
 \end{eqnarray}
where the prime indicates that the term $G=0$ should be ommited from
the sum.

@@

\subsection{Reflectance Measurement}
\label{sec:refl-meas}
We measured the reflectivity spectra at different positions over our
samples using a {\em Perkin Elmer Lambda 950}
UV-Vis-NIR spectrophotometer.\notaL{Finalmente, ¿fue éste el que se
  usó? Si sí, ¿hay algo internesante que decir sobre el? Cosas como el
tamaño de mancha, resolución espectral, etc.} For interpretation of the
data layer we used
the standard formula \cite{T8,T9} for the reflectance of three media:
air (0) environment, the PS film (1) and the c-Si substrate (2),
 \begin{equation}\label{Eq:ECMR}
   R=\left |\frac{r _ {_ {01}}r _ {_ {12}} e^{2i\psi}}{1+r _ {_
   {01}}r _ {_ {12}} e^{2i\psi}}\right |^2
\end{equation}
where $r_{01}$ and $r_{12}$ are the Fresnel reflectance
coefficients of the air/PS and PS/c-Si interfaces \cite{T10,T11}
and $\psi=k_1^\perp d$, where $k_1^\perp$ is
the component of the wavevector perpendicular to the surface within
the porous layer of thickness $d$. The reflectance depends on the
thickness of the film and on the index of refraction $n_1=n_{\text{PS}}$ of the porous
layer, which we relate to the porosity through Bruggeman's
effective medium theory \cite{I20},
\begin{equation}\label{Eq:Brugg}
 p\frac{1-\epsilon_1} {1+\epsilon_1} + (1-p)
  \frac{\epsilon_2 - \epsilon_1}
  {\epsilon_2+\epsilon_1}=0,
\end{equation}
where $\epsilon_2=\epsilon_{\text{Si}}$ is the dielectric function of
the c-Si substrate, and
$\epsilon_1=n_{\text{PS}}^2$ is the dielectric function of the PS layer.
We fitted the reflectance spectra using the porosity $p$ and the
thickness $d$ and a scale calibration factor $s$ as fitting
parameters, and thus, we obtained the porosity
$p$ and the etching rate $v=d/t$ for different values of the local
current density $j_\perp$ expected at several positions on different
samples.

@@

From Eq. \eqref{Eq:J} we evaluate the
normalized current density $j_\perp/I$ expected at the positions $n$ indicated in
Fig. \ref{fig:SI3}.
(Table \ref{t:xj}).
\begin{table}
  \centering
  \begin{tabular}{rrr}
    \(x'_n\)(cm) & \(x\)(cm)& \(j_\perp/I\) (\(\text{cm}^{-2})\)\\
    from edge& from wall&\\
    \hline
    0.2 & 0.06 & 0.722\\
    0.4 & 0.26 & 0.672\\
    0.6 & 0.46 & 0.577\\
    0.8 & 0.66 & 0.464\\
    1.0 & 0.86 & 0.360\\
    1.2 & 1.06 & 0.275\\
    1.4 & 1.26 & 0.211\\
    1.6 & 1.46 & 0.167\\
  \end{tabular}
  \caption{Normalized current density $j_\perp/I$ expected at different positions $x'_n$.}
  \label{t:xj}
\end{table}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{R5vslambda}
  \caption{Reflectance spectra at different positions
    ($x'_n=0.2-1.6\,\text{cm}$, $y=0.74\,\text{cm}$)
    on sample $G_1$ ($I_1=5\,\text{mA}$). We show
  experimental results and results fitted through
  equations~\eqref{Eq:ECMR} and \eqref{Eq:Brugg}}.
  \label{fig:R5}
\end{figure}
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{R10vslambda}
  \caption{Reflectance spectra at different positions
    ($x'_n=0.2-1.6\,\text{cm}$, $y=0.74\,\text{cm}$)
    on sample $G_2$ ($I_1=10\,\text{mA}$). We show
  experimental results and results fitted through
  equations~\eqref{Eq:ECMR} and \eqref{Eq:Brugg}}.
  \label{fig:R10}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{R20vslambda}
  \caption{Reflectance spectra at different positions
    ($x'_n=0.2-1.6\,\text{cm}$, $y=0.74\,\text{cm}$)
    on sample $G_3$ ($I_3=20\,\text{mA}$) (Fig. \ref{fig:SI3}),
    We show
    experimental results and results fitted through
    equations~\eqref{Eq:ECMR} and \eqref{Eq:Brugg}}.
  \label{fig:R20}
\end{figure}

We measured the reflectance spectra  at the positions indicated in
Fig. \ref{fig:SI3} on our three samples $G_1$, $G_2$,
and $G_3$, prepared using the same procedure
(Sec. \ref{sec:fabrication-ps-grin}) but applying different currents
$I_1=5\,\text{mA}$, $I_2=10\,\text{mA}$, and $I_3=20\,\text{mA}$, . The results are shown in
Figs. \ref{fig:R5}, \ref{fig:R10}, and \ref{fig:R20}.
We fitted the reflectance measurements using Eqs. \eqref{Eq:ECMR} and
\eqref{Eq:Brugg} using the local porosity $p$, and the thickness of the
film  $d$ as
adjustable parameters. We also fitted a scaling parameter $s$ to allow
for calibration variations among spectra. From the thickness we
obtained the etching rate $v=d/t$ at each position. Notice that the fits are reasonably
good. The contrast of the reflectance in the experiment is somewhat smaller
than in our fitted curves. We believe this is due to the finite width
\notaL{beams width=?} of the illuminating beam of our
spectrometer. Thus, as our GRIN sample is not macroscopically homogeneous and its
properties have a gradient, the
experimental results have contributions from regions with slightly
different porosities and thicknesses, averaging out the interference
maxima and minima. We expect microscopic inhomogeneities such as
interface roughness might also reduce the contrast through scattering
and its corresponding apparent dissipation \notaL{citar a Guille}.
The loss of contrast is most notable for the thicker regions
towards the left side of Fig. \ref{fig:SI3} and for smaller
wavelengths.

@@

\begin{table}
\centering
\begin{tabular}{lrrrrrr}
  Sample/ & position & density & porosity &
  thickness & scale & rate\\
  $I$ (mA) &$x'_n$ (cm)&  $j$ ($\text{mA}/\text{cm}^2$) & $p$
       & $d$ ($\mu\text{m}$) & $s$ & $v$ (nm/s)\\
\hline
$G_1$/ 5 &0.2 & 3.61 & 0.494 & 0.340 & 0.849&  1.361 \\
         &0.4 & 3.36 & 0.571 & 0.390 & 0.979&  1.558  \\
         &0.6  & 2.88& 0.566 & 0.331 & 0.957&  1.325 \\
         &0.8 & 2.32 & 0.556 & 0.273 & 0.954&  1.093 \\
         &1.0 & 1.80 & 0.559 & 0.227 & 0.995&  0.894 \\
         &1.2 & 1.37 & 0.556 & 0.189 & 0.973&  0.754 \\
         &1.4 & 1.06 & 0.549 & 0.151 & 0.961&  0.605 \\
         &1.6 & 0.83 & 0.552 & 0.124 & 0.990&  0.495 \\
$G_2$/10 &0.2 & 7.22 & 0.591 & 0.635 & 0.856&  2.539 \\
         &0.4 & 6.72 & 0.644 & 0.693 & 0.991&  2.774 \\
         &0.6 & 5.77 & 0.638 & 0.591 & 0.952&  2.363 \\
         &0.8 & 4.64 & 0.626 & 0.533 & 0.980&  2.131 \\
         &1.0 & 3.60 & 0.599 & 0.459 & 0.939&  1.835 \\
         &1.2 & 2.75 & 0.590 & 0.404 & 0.945&  1.618 \\
         &1.4 & 2.11 & 0.575 & 0.338 & 0.936&  1.351 \\
         &1.6 & 1.67 & 0.571 & 0.296 & 0.948&  1.183 \\
$G_3$/20 &0.2 &14.45 & 0.686 & 1.204 & 1.149&  4.818 \\
         &0.4 & 13.44 & 0.713 & 1.193 & 1.078&  4.772 \\
         &0.6 & 11.54 & 0.703 & 1.044 & 1.059&  4.177 \\
         &0.8 &  9.29 & 0.626 & 0.752 & 1.006&  3.006 \\
         &1.0 &  7.20 & 0.625 & 0.538 & 1.010&  2.152  \\
         &1.2 &  5.50 & 0.593 & 0.439 & 0.962&  1.755 \\
         &1.4 &  4.22 & 0.584 & 0.363 & 0.962&  1.453 \\
         &1.6 &  3.33 & 0.591 & 0.339 & 1.011&  1.357 \\
\end{tabular}
\caption{\label{t:jpdv}
  Current density and fitted parameters for saveral positions on
  three samples:  porosity, thickness, scale factor and etching rate.}
\end{table}

From the data in Table \ref{t:jpdv} we can plot the fitted porosity as
a function of the calculated density current, as shown for our three
samples in Fig. \ref{fig:p}.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{pvsj}
  \caption{Porosity as a function of current density for three samples
    $G_1$, $G_2$, $G_3$. The data points for each sample are joined by
    thick lines. The arrows point to data that correspond to
    position $x'_1=0.2\,\text{cm}$, joined to the other data by thin
    lines (see text). We include linear fits to the data from
    sample $G_3$ (thick straight line) and to that from all the
    samples (thin straight line). }
  \label{fig:p}
\end{figure}
Notice that for each sample the data points lie around straight lines,
except for one outlier point in each corresponding to position
$x'_1$. As discussed in Sec. \ref{sec:ps-grin-single}, those points
were very close to a wall of the electrolytic cell, so they were
affected by leakage currents towards the underside of the wall.
For this reason, we exclude those points from the following
analysis. We made a linear fit to the data from sample $G_3$ and to
the data from the three samples. A comparison shows that a fit to the
data of just one sample, $G_3$, turns out to be a reasonable predictor for the
porosity of all the samples.  From that fit we obtain that for our
preparation conditions
\begin{equation}\label{eq:p}
  p\approx 0.013\frac{\text{cm}^2}{\text{mA}} j_\perp+0.53.
\end{equation}

Similarly, we can plot the fitted etching rate as
a function of the calculated density current, as shown for our three
samples in Fig. \ref{fig:v}.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{vvsj}
  \caption{Etching rate as a function of current density for three samples
    $G_1$, $G_2$, $G_3$. The data points for each sample are joined by
    thick lines. The arrows point to data that correspond to
    position $x'_1=0.2\,\text{cm}$, joined to the other data by thin
    lines (see text). We include linear fits to the data from
    sample $G_3$ (thick straight line) and to that from all the
    samples (thin straight line). }
  \label{fig:v}
\end{figure}
As for the porosity, there are outlier points corresponding to the
immediate proximity of the wall of the cell, but the remaining points
lie on straight lines for each sample, and they
may all be approximated by a linear fit to the data of just one
sample, $G_3$, from which we get
\begin{equation}\label{eq:v}
  v\approx 0.35\frac{\text{cm}^2}{\text{mA}}
  \frac{\text{nm}}{\text{s}}j_\perp + 0.092\frac{\text{nm}}{{s}}.
\end{equation}

Using Eqs.  \eqref{Eq:ECMR}-\eqref{eq:v} we can calculate the
reflectance spectra for any
desired current density $j_\perp$ and etching time. This is
illustrated in Fig. \ref{fig:Rvsjl} for the parameters that correspond
to our samples.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{jlr}
  \caption{Reflection $R$ of a PS film as a function of the current density
    current $j_\perp$ and wavelength $\lambda$ for an etching time
    $t=250\,\text{s}$. Theory (left panel) and experiment (right
    panel, see text). We indicate with the numbers 1, 2, 3 the
    data corresponding to the corresponding samples $G_1$, $G_2$ and
    $G_3$.}
  \label{fig:Rvsjl}
\end{figure}
On the right hand side of the figure we display a quilt made by
patching together the experimental reflectance data corresponding to
Figs. \ref{fig:R5}- \ref{fig:R20}, ordered according to the
corresponding current density as presented in Table
\ref{t:jpdv}. Nevertheless, for the reasons mentioned above, we
eliminated the data corresponding to position $x'_1$ on all
samples. Furthermore, as the results corresponding to sample $G_2$ in
Figs. \ref{fig:p} and  \ref{fig:v} seem shifted with respect to those
of the other samples, in order to facilitate the visualization of the
results, we artificially shifted horizontally towards the
right their contributions to Fig. \ref{fig:Rvsjl} by
$1\,\text{mA}/\text{cm}^2$. Notice that the experimental results may
be grouped along bright and dark bands and that they correspond closely to
those expected theoretically, though the experimental bands are somewhat shifted,
especially for low current densities, and the minima are not as low.

The theoretical reflectance coudl as well be calculated using
\eqref{Eq:ECMR}-\eqref{eq:v} for more complicated structures, in which the
current $I$ is modulated in time, allowing the design and analysis of
non-trivial multilayered GRIN PS structures.
